NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE, PG and PS lipids

### 2017-08-23 Manuscript/manuscript.tex
All simulation results (at least wihtout ions) are now reported with signs. Experimental signs are then set to give best agreement with simulations, when data is not available (PE and PG).

\subsection{PE headgroup}
Absolute values of order parameters between Slipids simulations \cite{??}
and experiments for DPPE are shown in Fig. \ref{HGorderParametersPE}.
Glycerol bakcbone order parameters in Slipids are off from experiments,
as systematically observed in this and previous studies \cite{??}.
Alpha order parameter is too low, but beta shows apparent agreement
with experiments. However, the sign of beta order parameter is positive,
in contrast to PC where negative sign was measured. Thus, the the beta order
parameter agrees with experiment with the assumption that its sign is opposite
than for PC.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPE.eps}
  \caption{\label{HGorderParametersPE}
    Order parameters for DPPE headgroup and glycerol
    backbone from simulations with Slipids \cite{??} and experiments
    (DPPE from \cite{seelig76} and E.coliPE from \cite{gally81}).
    Absolute values are shown, because signs are not known experimentally.
  }
  \todo{Experimental signs of the order parameters would be highly useful.} \\
\end{figure}

@@

\subsection{PG headgroup}
Comparison between experiments and simulations with CHARMM GUI
parameters for PG lipids in Fig. \ref{HGorderParametersPOPG} suggest that
the model overestimates forking in $\gamma$ and $\alpha$ order parameters,
and magnitudes of $\beta$ and $g_1$ order parameters.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPG.eps}
  \caption{\label{HGorderParametersPOPG}
    Order parameters for PG headgroup and glycerol backbone from simulations with CHARMM GUI parameters and experiments without CaCl$_2$ 
    (POPG from \cite{borle85} contains 10mM of PIPES, DPPG from \cite{wohlgemuth80} contains 10mM PIPES and 100mM CaCl,
    E.Coli PG results from \cite{gally81}).
    Absolute values are shown, because signs are not known for experimental data.
    Glycerol backbone order parameters are negative in simulations, while $alpha$, $\beta$ and
    smaller $\gamma$ are positive.
  }
  \todo{More simulation data for lipids with different headgroups to be collected}
  \todo{CHARMM GUI simulation contains only counter ions as potassium.
    All experiments here contain some amount of sodium salt. The best
    ion concentrations for comparison should be figured out.}
  \todo{Experimental signs of the order parameters would highly useful.}
\end{figure}

>>>>

\subsection{PE headgroup}
Order parameters from Slipids simulations 
and experiments for DPPE are shown in Fig. \ref{HGorderParametersPE}.
Glycerol backbone order parameters in Slipids are off from experiments,
as already observed previously for PC lipids \cite{botan15}.
Order parameter signs for PE are not experimentally measured yet.
For headgroup the signs are set to give best agreement with simulations
and for glycerol to be consistent with experimental signs for PC.
Order parameter for $\beta$ carbon shows apparent agreement
with experiments. However, the sign of beta order parameter is positive,
in contrast to PC where negative sign was measured. Thus, the the beta order
parameter agrees with experiment with the assumption that its sign is opposite
than for PC. This is yet to be confirmed by experiments.
Order parameter for $\alpha$ carbon is too close to zero, even if the sign
would be correct.

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPE.eps}
  \caption{\label{HGorderParametersPE}
    Order parameters for DPPE headgroup and glycerol
    backbone from simulations with Slipids \cite{??} and experiments
    (DPPE from \cite{seelig76} and E.coliPE from \cite{gally81}).
    Absolute values are shown, because signs are not known experimentally.
  }
  \todo{Experimental signs of the order parameters would be highly useful.} \\
\end{figure}

@@

\subsection{PG headgroup}
Comparison between experiments and simulations for PG lipids is shown
in Fig. \ref{HGorderParametersPOPG}. The signs are not yet measured
experimentally. They are set to give the best argeement with experiments.
This would suggest that the $\beta$ order parameter would be positive,
in contrast to PC and PS headgroups, were negative signs were measured.
Even thought the signs turned out to be correct, the tested models would
not give a very good argeement with the experiments.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPG.eps}
  \caption{\label{HGorderParametersPOPG}
    Order parameters for PG headgroup and glycerol backbone from simulations and experiments without CaCl$_2$ 
    (POPG from \cite{borle85} contains 10mM of PIPES, DPPG from \cite{wohlgemuth80} contains 10mM PIPES and 100mM CaCl,
    E.Coli PG results from \cite{gally81}).
    Signs are not known for experimental data. They are determined to give best agreement
    with simulations. This is not reliable and should be corrected when experimental
    data becomes available.
  }
  \todo{More simulation data for lipids with different headgroups to be collected} \\
  \todo{CHARMM GUI simulation contains only counter ions as potassium.
    All experiments here contain some amount of sodium salt. The best
    ion concentrations for comparison should be figured out.} \\
  \todo{Experimental signs of the order parameters would highly useful.}
\end{figure}
